Hierarchically modelling \emph{Kepler} dwarfs and subgiants to improve inference of stellar properties with asteroseismology

### 2020-11-18 paper/main.tex
Updated and added to solar results

Out of the remaining 65 stars with results from the NP model, 2 stars were dropped from the PP model. A consequence of partially pooling parameters is that a population spread, $\sigma$ allows for individual parameters to vary outside of the prior range given to the population mean, $\mu$. In this case, individual stellar $\mlt$ was allowed to vary outside the range for which the ANN was valid if $\sigma_\alpha$ was large. The 2 removed stars happened to have high likelihoods outside of the valid $\mlt$ range. We found that removing the same 2 stars from the other models made negligible difference to the results, so we leave a solution to this problem to future work. Naturally, we did not see the same issue in the MP model, so we proceeded with modelling the same 65 stars as with the NP model.

@@

\section{The solar calibrator}\label{sec:sun-res}

We found that our model consistently recovers the Sun when modelled in each of the NP, PP and MP models. In Table \ref{tab:sun-out} we present the results for the Sun as a star from the NP model to show what we obtain without the influence of any other stars in the sample. We show the marginal and joint posterior distributions for the solar parameters from the NP model in the corner plot in Figure \ref{fig:sun-results}.

\begin{table}
    \centering
    \caption{Solar results from the NP model. The second column shows the median marginalised posterior samples for each parameter with their respective upper and lower 68 per cent credible intervals.}
    \label{tab:sun-out}
    \input{sun_outputs.tex}
\end{table}

>>>>

Out of the remaining 65 stars with results from the NP model, 2 stars were dropped from the PP model. A consequence of partially pooling parameters is that a population spread, $\sigma$ allows for individual parameters to vary outside of the prior range given to the population mean, $\mu$. In this case, individual stellar $\mlt$ was allowed to vary outside the range for which the ANN was valid if $\sigma_\alpha$ was large. The 2 removed stars happened to have high likelihoods outside of the valid $\mlt$ range. We found that removing the same 2 stars from the other models made negligible difference to the results, so we leave a solution to this problem to fu  ture work. Naturally, we did not see the same issue in the MP model, so we proceeded with modelling the same 65 stars as with the NP model.

@@

\section{The Sun as a star}\label{sec:sun-res}

Our model consistently recovers the Sun when modelled in each of the NP, PP and MP models. In Table \ref{tab:sun-out} we present the results for the Sun as a star from the NP model to show what we obtain without the influence of any other stars in the sample. We show the marginal and joint posterior distributions for the solar parameters from the NP model in the corner plot in Figure \ref{fig:sun-results}.

We found some differences between $\mlt$ from our solar model and solar calibrations in the literature produced using \textsc{MESA} with similar input physics. For example, the solar calibration in \citet{Stancliffe.Fossati.ea2016} using \citet{Asplund.Grevesse.ea2009} abundances yields compatible initial abundances, $Z_\mathrm{init} = 0.0149$ and $Y_\mathrm{init} = 0.266$ but $\mlt = 1.783$ which differs from our results by about 10-$\sigma$. This is likely because of a few differences in observed values used for the calibration. \citet{Stancliffe.Fossati.ea2016} used observed helium abundance and convection zone depth measurements from helioseismology. Furthermore, solar calibrations typically include convective envelope overshooting. Presuming overshooting increases mixing in the star, we might expect a lower $\mlt$ to compensate this. Therefore, we stress that the addition of the Sun as a star in our model is with the assumption of our choice of input physics.

\begin{table*}
    \centering
    \caption{Solar results from the NP model. The second column shows the median marginalised posterior samples for each parameter with their respective upper and lower 68 per cent credible intervals.}
    \label{tab:sun-out}
    \input{sun_outputs.tex}
\end{table*}
